Title

### 2012-07-10 inc/external_forces/external_forces.tex
Split AG model chapter into two different chapters, one for previous efforts and one for my contributions.

@@

In the longitudinal ($ z $) direction, a resonant radio-frequency (RF) cavity can be used in a UEM column or UED experiment \cite{oudheusden_electron_2007,fill_sub-fs_2006} to act as a pulse compression or `temporal focusing' element.
Although there are many possible resonant cavity structures,\cite{oudheusden_electron_2007,humphries_principles_1986} for simplicity, this analysis will consider only the evacuated cylindrical (or `pillbox') $\text{TM}_{010}$ cavity for which the electrons propagate down the axis.\cite{fill_sub-fs_2006,humphries_principles_1986}
The known mathematical forms of the electric and magnetic components of this resonant mode together with a super-Gaussian envelope function (\ref{eq:reg_of_influence}) allow the three main effects of a pill-box RF cavity element on the electron pulse to be described within the approximation of the linear force extension to the AG model: the primary action of the pulse compression (or acceleration and expansion dependent upon the relative RF phase), and the transverse lens effects due to the magnetic component of the $\text{TM}_{010}$ resonance and the electric RF cavity fringe fields at its entrance and exit apertures.\cite{kim_rf_1989}

>>>>

A magnetic lens may be modeled using one linear force contribution.
Unfortunately, it is not practical to write an analytic form of the magnitude of this term; the field distribution is very complicated to describe\cite{montgomery_some_1961} and the ``lensing'' action is actually a compound force (first rotating the beam, then lensing).
We have found that in practice, characterizing a specific magnetic lens ($M_{\smallT}(I)$ where $I$ is the current in the magnetic lens) is much easier than attempting to find a generic functional form.

@@

In the longitudinal ($ z $) direction, a resonant radio-frequency (RF) cavity can be used in a UEM column or UED experiment \cite{oudheusden_electron_2007,fill_sub-fs_2006} to act as a pulse compression or `temporal focusing' element.
The model of the RF cavity is different from the magnetic lens in two distinct ways.
First, the RF cavity contains several different fields and thus contributes several different linear force terms to the overall equation set.
Second, though there are more terms, their magnitudes are easily connected to the physical characteristics of the cavity.

Although there are many possible resonant cavity structures,\cite{oudheusden_electron_2007,humphries_principles_1986} for simplicity, this analysis will consider only the evacuated cylindrical (or `pillbox') $\text{TM}_{010}$ cavity for which the electrons propagate down the axis.\cite{fill_sub-fs_2006,humphries_principles_1986}
The known mathematical forms of the electric and magnetic components of this resonant mode together with a super-Gaussian envelope function (\ref{eq:reg_of_influence}) allow the three main effects of a pill-box RF cavity element on the electron pulse to be described within the approximation of the linear force extension to the AG model: the primary action of the pulse compression (or acceleration and expansion dependent upon the relative RF phase), and the transverse lens effects due to the magnetic component of the $\text{TM}_{010}$ resonance and the electric RF cavity fringe fields at its entrance and exit apertures.\cite{kim_rf_1989}
